---
title: '**Supplementary Figures**'
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: null
  latex_engine: pdflatex
  html_document:
    df_print: paged
---

# Nutrient production by coral reef fishes

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS1.pdf"); i = i + 1
```

**Fig. S`r i`. Association between nutrient concentrations and growth potential of 541 coral reef fish species.** Points are individual species observed across Belize, Fiji, Madagascar, and the Solomon Islands. Nutrient concentrations are per 100 g of white muscle tissue, for calcium, iron, selenium, zinc, omega-3 fatty acids and vitamin A. The growth coefficient Kmax is the value of growth coefficient K for each species at its theoretical maximum size, derived from the von Bertalanffy equation.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_benthic_cov.pdf"); i = i + 1
```

**Fig. S`r i`. Association between hard coral and other dominant habitat groups.** In (a), points are hard coral cover at each reef, against cover of macroalgae, rubble, and turf algae, annotated with simple linear regression fits. In (b), points are slope estimates for relationships between hard coral and each dominant benthic group, from a simple linear regression, with 95% confidence intervals.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_nutprod_gradients.pdf"); i = i + 1
```

**Fig. S`r i`. Contribution to nutrient production by fishery target groups along gradient in fishable biomass.** Percent contribution to production of six nutrients along fishable biomass gradients in each country. Lines are posterior median values with 95% highest posterior density intervals, for herbivores (green), piscivores (blue) and mobile invertivores (orange). 

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX.pdf"); i = i + 1
```

**Fig. S`r i`. Effect of benthic cover covariates on trophic structure of nutrient production.** Points are median posterior effects of each covariate on each of the three trophic groups (herbivores, mobile invertivores, piscivores), with 95% highest posterior density intervals. 